\documentclass[11pt]{article}
\usepackage{graphicx}    % needed for including graphics e.g. EPS, PS
\usepackage{epstopdf}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{xspace}
\usepackage{mathtools}
\usepackage{tikz}
\usepackage{epsfig}
\usepackage{float}
\usepackage{natbib}
\usepackage{subfigure}
\usepackage{setspace}
\usepackage{tabularx,ragged2e,booktabs,caption}


\setlength{\oddsidemargin}{0.1in}
\setlength{\textwidth}{7.25in}

\setlength{\topmargin}{-1in}     %\topmargin: gap above header
\setlength{\headheight}{0in}     %\headheight: height of header
\setlength{\topskip}{0in}        %\topskip: between header and text
\setlength{\headsep}{0in}        
\setlength{\textheight}{692pt}   %\textheight: height of main text
\setlength{\textwidth}{7.5in}    % \textwidth: width of text
\setlength{\oddsidemargin}{-0.5in}  % \oddsidemargin: odd page left margin
\setlength{\evensidemargin}{0in} %\evensidemargin : even page left margin
\setlength{\parindent}{0.25in}   %\parindent: indentation of paragraphs
\setlength{\parskip}{0pt}        %\parskip: gap between paragraphs
\setlength{\voffset}{0.5in}


% Useful commands:

% \hfill		aligns-right everything right of \hfill

\begin{document}
\doublespacing
\title{Magnetohydrodynamic Object-Oriented Numerical Simulation (MOONS)}
\author{C. Kawczynski \\
Department of Mechanical and Aerospace Engineering \\
University of California Los Angeles, USA\\
}
\maketitle

\section{Stencils for first derivatives}
This document uses results from the non-uniform grid stencil results.

\subsection{Staggered}
By staggered derivative, what is meant is

if the field $f\in CC$ then $\frac{\partial f}{\partial h}\in N$.  

Likewise

if the field $f\in N$ then $\frac{\partial f}{\partial h}\in CC$.  

Where $CC$ and $N$ mean cell center and cell corner data. To put in words, if data lives on the primary grid, then its derivative lives on the dual grid. That is what a staggered derivative means in MOONS.

\begin{equation}
	f_{p,i+1/2}' = \frac{f_{p,i+1}-f_{p,i}}{h_{p,i+1}-h_{p,i}} \qquad i=1,sf-1
\end{equation}

Where the subscript $p$ means primary grid, and $sf$ means the size of $f$. Note that the half index is used. To remove the half index, we may write this as

\begin{equation}
	f_{d,i+gt}' = \frac{f_{p,i+1}-f_{p,i}}{h_{p,i+1}-h_{p,i}} \qquad i=1,sf-1
\end{equation}

Where
 \begin{equation}
   gt = gridType = 
  \begin{cases} 
      0 & \text{if $f \in $ cell center} \\
      1 & \text{if $f \in $ cell corner} \\
   \end{cases}
\end{equation}
Note that the result, $f'$, lives on the dual grid (hence the subscript $d$). Also note that $f'$ is not defined for the ghost cell ($f_1'$). MOONS sets ghost cells to be zero when computing derivatives, the applyBCs module sets these cells to enforce BCs.


\subsection{Collocated}
For the collocated case (when both $f$ and $\frac{\partial f}{\partial h}$ live on the primary grid), MOONS uses the results from the non-uniform grid-stencils. 

THESE FORMULAS NEED TO BE CHECKED FOR CC VS NODE DATA SINCE THERE EXISTS A GHOST CELL. THIS VERY WELL MAY CHANGE THE NECESSARY INDEX FOR CC VS N DATA. THIS SHOULD BE SIMPLE TO FIX, SIMPLY ADD A gt TO THE INDEXING FOR $\alpha_k$ and $\beta_j$.

\subsubsection{Central differencing}

Use the non-uniform grid stencil results with

\begin{equation}
	\alpha_k = -(x_{i} - x_{i-1}) = \Delta x_{i} \qquad k = -1
\end{equation}
\begin{equation}
	\beta_j = (x_{i+1} - x_{i}) = \Delta x_{i+1} \qquad j = 1
\end{equation}


\subsubsection{Forward differencing (soon to be obsolete)}

Use the non-uniform grid stencil results with

\begin{equation}
	\alpha_k = -(x_{i+1} - x_{i}) = \Delta x_{i+1} \qquad k = 1
\end{equation}
\begin{equation}
	\beta_j = x_{i+2} - x_{i} = (x_{i+2} - x_{i+1}) + (x_{i+1} - x_{i}) = \Delta x_{i+1} + \Delta x_{i+2} \qquad j = 2
\end{equation}

\subsubsection{Backward differencing (soon to be obsolete)}

Use the non-uniform grid stencil results with

\begin{equation}
	\alpha_k = -(x_{i} - x_{i-1}) = -\Delta x_{i} \qquad k = -1
\end{equation}
\begin{equation}
	\beta_j = -(x_{i} - x_{i-2}) = -(\Delta x_{i} + \Delta x_{i-1}) \qquad j = -2
\end{equation}

\end{document}


