\documentclass[11pt]{article}
\newcommand{\PSCHAIN}{..}
\input{../prepend_PS_chain}
\newcommand{\rootdir}{\PSCHAIN}
\input{\PSCHAIN/includes/includes}


\begin{document}
\doublespacing
\MOONSTITLE
\maketitle

\section{applyBCs for sn less than sc}

This document describes how the applyBCs module works. Succinctly, when called, it defines the ghost values of a field such that the boundary conditions are enforced.

\section{Dirichlet}
For wall coincident Dirichlet BCs, the boundary values themselves are prescribed in addition to the ghost values.

\subsection{Direct (wall coincident)}
Trivial assignment
\begin{equation}
u = u_{bc}
\end{equation}

\subsection{Interpolated (Wall incoincident)}
Ghost values mirror about the boundary value. In order to do this, slopes are matched from the ghost cell to the first interior cell using the prescribed boundary value.

\subsubsection{General}
\begin{equation}
	\frac{u_{ghost}-u_{interior}}{h_{ghost}-h_{interior}}
	=
	\frac{u_{wall}-u_{interior}}{h_{wall}-h_{interior}}
\end{equation}
Solving for the ghost values we have
\begin{equation}
	u_{ghost}
	=
	u_{interior} + \alpha (u_{wall}-u_{interior})
\end{equation}
\begin{equation}
	=
	u_{wall}\alpha + u_{interior}(1-\alpha)
\end{equation}
Where
\begin{equation}
	\alpha = \frac{h_{ghost}-h_{interior}}{h_{wall}-h_{interior}}
\end{equation}

% \subsubsection{Forward}
% \begin{equation}
% \frac{u_{c,1}-u_{c,2}}{h_{c,1}-h_{c,2}} = \frac{u_{wall}-u_{c,2}}{h_{n,1}-h_{c,2}}
% \end{equation}
% Solving for $u_1$ yields
% \begin{equation}
% 	u_{c,1} = u_{c,2} + \frac{h_{c,1}-h_{c,2}}{h_{n,1}-h_{c,2}}(u_{wall}-u_{c,2})
% \end{equation}

% \subsubsection{Backward}
% \begin{equation}
% \frac{u_{c,sc}-u_{c,sc-1}}{h_{c,sc}-h_{c,sc-1}} = \frac{u_{n,sn}-u_{c,sc-1}}{h_{n,sn}-h_{c,sc-1}}
% \end{equation}
% Solving for $u_{sc}$ yields
% \begin{equation}
% 	u_{c,sc} = u_{c,sc-1} + \frac{h_{c,sc}-h_{c,sc-1}}{h_{n,sn}-h_{c,sc-1}}(u_{n,sn}-u_{c,sc-1})
% \end{equation}

\section{Neumann}
% \subsection{Direct (wall coincident) $~O(dh^2)$}
\subsection{Direct (wall coincident) ~O(dh2)}
A 2nd order accurate, one sided difference equation is used to approximate the derivative. The boundary value is then solved for.

\subsection[alternative title goes here]{The values of $\beta$ for which $\omega_i$ is defined at the origin}

\subsubsection{Forward differencing}
Let
\begin{equation}
	\alpha_k = h_{n,2} - h_{n,1} \qquad k = 1
\end{equation}
\begin{equation}
	\beta_j = h_{n,3} - h_{n,1} \qquad j = 2
\end{equation}
And use the one sided difference equation
\begin{equation}
	f_i = \frac{f_i' (\beta_j - \alpha_k) - \frac{\beta_j}{\alpha_k} f_{i+k} + \frac{\alpha_k}{\beta_j} f_{i+j}}{\frac{\alpha_k}{\beta_j} - \frac{\beta_j}{\alpha_k}}
\end{equation}
\subsubsection{Backward differencing}
Let
\begin{equation}
	\alpha_k = -(h_{n,sn} - h_{n,sn-1})  \qquad k = -1
\end{equation}
\begin{equation}
	\beta_j = -(h_{n,sn} - h_{n,sn-2})  \qquad j = -2
\end{equation}
And use the one sided difference equation
\begin{equation}
	f_i = \frac{f_i' (\beta_j - \alpha_k) - \frac{\beta_j}{\alpha_k} f_{i+k} + \frac{\alpha_k}{\beta_j} f_{i+j}}{\frac{\alpha_k}{\beta_j} - \frac{\beta_j}{\alpha_k}}
\end{equation}

\subsection{Direct (wall coincident) ~O(dh)}
These are onee sided, $~O(\Delta h)$, equations. They are probably not the best BCs to use (use $~O(\Delta h^2)$ formulas instead. These equations are simple and should provide a simple check.
\subsubsection{Forward differencing}
\begin{equation}
	\frac{u_{n,1}-u_{n,2}}{h_{n,1}-h_{n,2}} = g
\end{equation}
Where $g$ is the slope at the boundary wall. Solving for $u_{n,1}$ we have
\begin{equation}
	u_{n,1} = u_{n,2} + (h_{n,1}-h_{n,2})g
\end{equation}
\subsubsection{Backward differencing}
\begin{equation}
	\frac{u_{n,sn}-u_{n,sn-1}}{h_{n,sn}-h_{n,sn-1}} = g
\end{equation}
Where $g$ is the slope at the boundary wall. Solving for $u_{n,sn}$ we have
\begin{equation}
	u_{n,sn} = u_{n,sn-1} + (h_{n,sn}-h_{n,sn-1})g
\end{equation}

\subsection{Direct (wall incoincident) ~O(dh2)}
Since the boundary is between 2 incoincident data points, the stencil is symmetric about the boundary and appears simple
\subsubsection{Forward differencing}
\begin{equation}
	\frac{p_1-p_2}{h_{c,1}-h_{c,2}} = p_{wall}'
\end{equation}
\begin{equation}
	p_1 = p_2 + (h_{c,1} - h_{c,2}) p_{wall}'
\end{equation}
\subsubsection{Backward differencing}
\begin{equation}
	\frac{p_{c,sc}-p_{c,sc-1}}{h_{c,sc}-h_{c,sc-1}} = p_{wall}'
\end{equation}
\begin{equation}
	p_{c,sc} = p_{c,sc-1} + (h_{c,sc} - h_{c,sc-1}) p_{wall}'
\end{equation}



\section{Robin}
Robin BCs are used for the tangential component of the magnetic field, which are wall incoincident.
So we will only derive these BCs.

\subsection{Interpolated (Wall incoincident)}
First, let $i,g,b$ indicate interior, ghost and boundary nodes respectively.

Analytic BCs:
\begin{equation}\begin{aligned}
	u + c \frac{\PD u}{\PD h} = 0 \\
	u =-c \frac{\PD u}{\PD h} \\
\end{aligned}\end{equation}
After discretizing, we have
\begin{equation}\begin{aligned}
	\frac{\PD u}{\PD h} = \frac{u_g - u_i}{dh} n, \qquad \text{n = 1 at xmax,ymax,zmin and n = -1 at xmin,ymin,zmin} \\
	u_b = \frac{u_g+u_i}{2} \\
\end{aligned}\end{equation}
Therefore, our discrete equation is
\begin{equation}\begin{aligned}
	\frac{u_g+u_i}{2} = -cn \frac{u_g - u_i}{dh} \\
	u_g = -u_i + 2cn \frac{u_i}{dh} - 2cn \frac{u_g}{dh} \\
	u_g \left( 1 + \frac{2 cn}{dh} \right) = u_i \left( -1 + \frac{2cn}{dh} \right) \\
\end{aligned}\end{equation}
Leaving us with
\begin{equation}
	\boxed{
	u_g = u_i \frac{\left(\frac{2cn}{dh} - 1 \right)}{\left(1 + \frac{2cn}{dh} \right)},
	\qquad \left(1 + \frac{2cn}{dh} \right) \ne 0, \qquad \text{(n may be negative)}
	}
\end{equation}

\end{document}