\newcommand{\toth}{\tiny{Toth, Gabor. "The $\DIV \B = 0$ constraint in shock-capturing magnetohydrodynamics codes." J. Comput. Phys. 161.2 (2000): 605-652.}}
\newcommand{\pattison}{\tiny{M. J. Pattison, K. N. Premnath, N. B. Morley, M. Abdou, Fusion Eng. Des. 83 (2008) 557-572.}}
\newcommand{\gujStella}{\tiny{G. Guj, F. Stella, J. Comput. Phys. 298 (1993) 286-298.}}
\newcommand{\bandaru}{\tiny{V. Bandaru, J. Pracht, T. Boeck, J. Schumacher, Theor. Comp. Fluid Dyn. (2015).}}
\newcommand{\guermond}{\tiny{Guermond, J. L., J. Léorat, and C. Nore. "A new Finite Element Method for magneto-dynamical problems: two-dimensional results." European Journal of Mechanics-B/Fluids 22.6 (2003): 555-579.}}
\newcommand{\kawczynski}{\tiny{C. Kawczynski, S. Smolentsev, M. Abdou. "A Lid-Driven Cavity MHD Flow Numerical Study at Moderate Magnetic Reynolds Number using Proper Magnetic Boundary Conditions". In Progress.}}
\newcommand{\roache}{\tiny{P. J. Roache, Annu. Rev. Fluid Mech. 29 (1997) 123-160.}}
\newcommand{\hunt}{\tiny{J. C. R. Hunt, J. Fluid Mech. 21 (1965) 577-590.}}
\newcommand{\shercliff}{\tiny{J. A. Shercliff, Proc. Camb. Phil. Soc. 49 (1953) 136.}}
\newcommand{\turner}{\tiny{Turner, Larry R. "Electromagnetic computations for fusion devices." IEEE Transactions on Magnetics 26.2 (1990): 847-852.}}
\newcommand{\kotulskiA}{\tiny{Kotulski, Joseph D., et al. "Electromagnetic analysis of forces and torques on the baseline and enhanced ITER shield modules due to plasma disruption." IEEE Transactions on Plasma Science 38.4 (2010): 1047.}}
\newcommand{\kotulskiB}{\tiny{Kotulski, Joseph D., Rebecca Coats, and Michael Ulrickson. "The analysis of the electromagnetic loads on selected ITER blanket shield modules due to induced eddy and halo currents." Fusion Engineering (SOFE), 2011 IEEE/NPSS 24th Symposium on. IEEE, 2011.}}
\newcommand{\iskakov}{\tiny{Iskakov, A. B., S. Descombes, and E. Dormy. "An integro-differential formulation for magnetic induction in bounded domains: boundary element-finite volume method." J. Comput. Phys. 197.2 (2004): 540-554.}}
\newcommand{\mikeulrickson}{\tiny{We received numerical data from Dr. Mike Ulrickson, computed from the plasma code DINA.}}
\newcommand{\Leriche}{Leriche, E. \& Gavrilakis, S. Direct numerical simulation of the flow in a lid-driven cubical cavity. Phys. Fluids 12, (2000).}
\newcommand{\Brackbill}{\tiny{Brackbill, Jeremiah U., and Daniel C. Barnes. "The effect of nonzero $\DIV \B = 0$ on the numerical solution of the magnetohydrodynamic equations." Journal of Computational Physics 35.3 (1980): 426-430.}}
\newcommand{\Leuer}{\tiny{Leuer, J. A., and J. C. Wesley. "ITER plasma start-up modeling." Fusion Engineering, 1993., 15th IEEE/NPSS Symposium on. Vol. 2. IEEE, 1993.}}
